### 2015-01-14 fundamentals/impl.tex
intro to simulation assistance. I'm still not sure about the title...

\subsection{Simulation Assistance}
\TODO{section intro needed}
To assist beginner users and developers in accomplishing working simulations
in the shortest time possible,

>>>>

\subsection{Simulation Assistance}
So that users and developers can build working simulations
in the shortest time possible, the \Cyclus ecosystem provides the fundamental 
building blocks: basic archetypes and a toolkit of commonly needed functions.
The \Cycamore library provides a suite of fundamental Region, Institution, and 
Facility archetypes, while the \Cyclus toolkit provides assistance to 
developers.
